Hydra Battles and Cie

### 2021-05-15 doc/part-hydras.tex
minor changes
proof that the length  of hydra battles is not primitive recursive
Fix references to fast growing hierarchies

\section{The Wainer hierarchy (functions \texorpdfstring{$F_\alpha$}{F\_alpha})}
\label{sect:wainer}

@@

The Wainer hierarchy~\cite{BW85, Wainer1970, KS81}, is also a family of fast growing functions, indexed by ordinals below $\epsilon_0$, by the following equations:

@@

A first attempt is to write a definition of $F_\alpha$ by equations, in the same as for $H\_alpha$.  We use the functional \texttt{iterate} defined in 
Module~\href{../theories/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}.

@@

Theorem F_alpha_beta alpha : 
   forall beta n, Canon_plus n alpha beta -> 
                                        F_ beta n <= F_ alpha n.
\end{Coqsrc}

>>>>

\section{A variant of the Wainer hierarchy (functions \texorpdfstring{$F_\alpha$}{F\_alpha})}
\label{sect:wainer}

@@

Ketonen and Solovay introduce in~\cite{KS81} a ``trivial'' variant of the Wainer hierarchy~\cite{BW85, Wainer1970} of fast growing functions, indexed by ordinals below $\epsilon_0$.

@@

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f\_alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$. A module about 
the classic Wainer hierarchy is in preparation.
\end{remark}

A first attempt is to write a definition of $F_\alpha$ by equations, in the same way as for $H\_alpha$.  We use the functional \texttt{iterate} defined in 
Module~\href{../theories/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}.

@@

Theorem F_restricted_mono_l alpha : 
   forall beta n, Canon_plus n alpha beta -> 
                                        F_ beta n <= F_ alpha n.
\end{Coqsrc}
